The SMT Competition 2015--2018

### 2019-08-30 2018/report/table-winners-unsat-core.tex
UC track was experimental (hence non-competitive) in 2016

       Division       & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2016                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2017                              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2018                          } \\

@@

       ALIA       & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\

@@

       AUFLIA     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
       AUFLIRA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
       AUFNIRA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
       BV         & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
       LIA        & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{veriT}                       } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
       LRA        & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{veriT}                       } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
       NIA        & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \nonc \cc{cvc4} CVC4 & \nonc \cc{cvc4} CVC4 \nc{Z3}                                      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
       NRA        & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
       QF\_ABV    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices             } \\

@@

       QF\_ALIA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices \nc{Z3}     } \\
       QF\_ANIA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
       QF\_AUFBV  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nc{Z3}                           } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{MathSAT} } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices \nc{MathSAT}} \\
       QF\_AUFLIA & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4                    } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4                } \\
       QF\_AUFNIA & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
       QF\_AX     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices             } \\
       QF\_BV     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nc{MathSAT}                      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{MathSAT} } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices             } \\
       QF\_BVFP   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nc{Z3}                           } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \nc{Z3}                     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\

@@

       QF\_FP     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nc{MathSAT}                      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \nc{Z3}                     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
       QF\_IDL    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}            } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}        } \\
       QF\_LIA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \cc{smti} SMTInterpol & \cc{smti} SMTInterpol \nc{Z3}                                    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol         } \\
       QF\_LIRA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}            } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}        } \\
       QF\_LRA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol             } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol             } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol         } \\
       QF\_NIA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
       QF\_NIRA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
       QF\_NRA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
       QF\_RDL    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{veriT}  } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}            } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}        } \\
       QF\_UF     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{MathSAT}} & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4                    } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4                } \\
       QF\_UFBV   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nc{MathSAT}                      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{MathSAT} } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices \nc{Z3}     } \\
       QF\_UFIDL  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices             } \\
       QF\_UFLIA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{MathSAT}} & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3} } \\
       QF\_UFLRA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{MathSAT}} & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices \nc{MathSAT}} \\
       QF\_UFNIA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
       QF\_UFNRA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
       UF         & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
       UFBV       & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\

@@

       UFIDL      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
       UFLIA      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
       UFLRA      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
       UFNIA      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\

>>>>

       Division       & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc 2016                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2017                              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2018                          } \\

@@

       ALIA       & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\

@@

       AUFLIA     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
       AUFLIRA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
       AUFNIRA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
       BV         & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
       LIA        & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{veriT}                       } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
       LRA        & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{veriT}                       } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
       NIA        & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \nonc \cc{cvc4} CVC4 & \nonc \cc{cvc4} CVC4 \nc{Z3}                                      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
       NRA        & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
       QF\_ABV    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices             } \\

@@

       QF\_ALIA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \cc{smti} SMTInterpol \nc{Z3}    } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices \nc{Z3}     } \\
       QF\_ANIA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
       QF\_AUFBV  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{MathSAT} } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices \nc{MathSAT}} \\
       QF\_AUFLIA & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \cc{smti} SMTInterpol \nc{Z3}    } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4                    } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4                } \\
       QF\_AUFNIA & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
       QF\_AX     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \cc{smti} SMTInterpol \nc{Z3}    } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices             } \\
       QF\_BV     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{MathSAT}                     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{MathSAT} } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices             } \\
       QF\_BVFP   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \nc{Z3}                     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\

@@

       QF\_FP     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{MathSAT}                     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \nc{Z3}                     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
       QF\_IDL    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \cc{smti} SMTInterpol \nc{Z3}    } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}            } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}        } \\
       QF\_LIA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \cc{smti} SMTInterpol \nc{Z3}    } & \cc{smti} SMTInterpol & \cc{smti} SMTInterpol \nc{Z3}                                    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol         } \\
       QF\_LIRA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \cc{smti} SMTInterpol \nc{Z3}    } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}            } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}        } \\
       QF\_LRA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \cc{smti} SMTInterpol            } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol             } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol         } \\
       QF\_NIA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                         } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
       QF\_NIRA   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                         } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
       QF\_NRA    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                         } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
       QF\_RDL    & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \cc{smti} SMTInterpol \nc{veriT}  } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}            } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 \nc{Z3}        } \\
       QF\_UF     & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \cc{smti} SMTInterpol \nc{MathSAT}} & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4                    } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4                } \\
       QF\_UFBV   & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{MathSAT}                      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{MathSAT} } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices \nc{Z3}     } \\
       QF\_UFIDL  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices             } \\
       QF\_UFLIA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \cc{smti} SMTInterpol \nc{MathSAT}} & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{Z3} } \\
       QF\_UFLRA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \cc{smti} SMTInterpol \nc{Z3}     } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{smti} SMTInterpol \nc{MathSAT}} & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices \nc{MathSAT}} \\
       QF\_UFNIA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
       QF\_UFNRA  & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
       UF         & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
       UFBV       & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\

@@

       UFIDL      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
       UFLIA      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
       UFLRA      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}      } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4 \nc{Z3}  } \\
       UFNIA      & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{ \nonc \nc{Z3}                          } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4              } & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\nonc \cc{cvc4} CVC4          } \\
